Preregistration analysis, Cost 2 study

### 2019-05-09 Cost2/Cost2_prereg.Rmd
matching plot styles mor

corrplot(mixCoeffs, 
         is.corr = F, 
         p.mat = mixPvals, 
         #type = "upper",
         outline = T,
         insig = "p-value",
         sig.level = -1, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

@@

``` {r 16.2.3. Plot logistic model, echo=FALSE,fig.align="center",fig.width=6,fig.height=6}
# par(mfrow=c(1,1))
# ## Plotting the winning model (colors are messed up)
# rewards <- seq(1,20,length = 1000)
# # wait
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",
#           handling = 2, 
#           reward = rewards, 
#           plotType = plot, 
#           color = cols[1],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",          
#           handling = 10, 
#           reward = rewards, 
#           color = cols[1],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",          
#           handling = 14, 
#           reward = rewards, 
#           color = cols[1])
# 
# 
# # cognitive
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[2],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[2],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[2])
# 
# 
# # physical
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[3],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[3],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[3])
# 
# # easy
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[4],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[4],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[4])
# 
# # title
# title("Probabilities for All Handling-Reward Combinations \n for Each Group")
# 
# # x axis
# xticks <- c(0,min(rewards[rewards>4]),min(rewards[rewards>8]),20)
# axis(1,at = xticks,c(0,4,8,20))
# 
# # legend
# legend("bottomright",
#        c("Wait: 2s","Wait: 10s","Wait: 14s",
#          "Cognitive: 2s","Cognitive: 10s","Cognitive: 14s",
#          "Physical: 2s","Physical: 10s","Physical: 14s",
#          "Easy: 2s","Easy: 10s","Easy: 14s"), 
#        fill = c(cols[1],cols[1],cols[1],cols[2],cols[2],cols[2],cols[3],cols[3],cols[3],cols[4],cols[4],cols[4]),
#        lty = rep(c(6,3,1,8),3),
#        cex = 0.8)
# 
# 
# # actual proportions (maybe, maybe not)
# # points(c(5,10,25),trueProp$propComplete[1:3], col = cols[1], pch=17) # wait
# # points(c(5,10,25),trueProp$propComplete[4:6], col = cols[1], pch=17)
# # points(c(5,10,25),trueProp$propComplete[7:9], col = cols[1], pch=17)
# # 
# # points(c(5,10,25),trueProp$propComplete[19:21], col = cols[2], pch=17) # cog effort
# # points(c(5,10,25),trueProp$propComplete[22:24], col = cols[2], pch=17)
# # points(c(5,10,25),trueProp$propComplete[25:27], col = cols[2], pch=17)
# # 
# # points(c(5,10,25),trueProp$propComplete[10:12], col = cols[3], pch=17) # phys effort
# # points(c(5,10,25),trueProp$propComplete[13:15], col = cols[3], pch=17)
# # points(c(5,10,25),trueProp$propComplete[16:18], col = cols[3], pch=17)
# 
# # and the residuals
# # plot(logisComb$residuals,
# #      main = "Residuals for the Logistic Regression",
# #      xlab = "trial",
# #      ylab = "Residuals")
# # 

@@

``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}

temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Half) %>%
  summarise(pAccepted = mean(Choice)) %>%
  ungroup() %>%
  spread(Half, pAccepted)

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
(prepost$plot <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID, Cost) %>%
                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                geom_point(size = 3, pch = 21, color = "black") +
                scale_fill_manual(values = cols) +
                xlim(0,1) +
                ylim(0,1) +
                geom_abline(slope = 1, intercept = 0, lty = 2) +
                theme(panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(),
                      axis.line = element_line(colour = "black"),
                      text = element_text(size = 16)))
```

>>>>

corrplot(mixCoeffs, 
         is.corr = F, 
         p.mat = mixPvals, 
         type = "upper",
         outline = T,
         insig = "p-value",
         sig.level = -1, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

@@

@@

``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# divide the data into proportion accepted before/after the break (one per column)
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost, Half) %>%
  summarise(pAccepted = mean(Choice)) %>%
  ungroup() %>%
  spread(Half, pAccepted)

@@

``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# scatter plot of pre/post acceptances
prepost$scatterplot <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID, Cost) %>%
                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                  geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                  scale_fill_manual(values = cols) +
                  xlim(0,1) +
                  ylim(0,1) +
                  labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                  geom_abline(slope = 1, intercept = 0, lty = 2) +
                  theme(panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        panel.background = element_blank(),
                        axis.line = element_line(colour = "black"),
                        text = element_text(size = 16))

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost$propBlocks <- dataAll %>%
 filter(Choice < 2) %>%
 group_by(SubjID, Cost, Block) %>%
 summarise(propAccept_subj = mean(Choice)) %>%
 group_by(Cost, Block) %>%
 summarize(propAccept = mean(propAccept_subj),
           seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
 ggplot(aes(Block, propAccept, fill = Cost)) +
   geom_point(size = 2, pch = 21, color = "black") +
   geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
   geom_line(aes(color = Cost)) +
   ylim(0, 1) +
   labs(y = "Proportion Acccepted") +
   scale_x_continuous(breaks = seq(6)) +
   scale_color_manual(values = cols) +
   scale_fill_manual(values = cols) +
   theme(legend.key = element_blank(),
         legend.position = c(0.8, 0.25),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"),
         text = element_text(size = 16))

grid.arrange(prepost$scatterplot, prepost$propBlocks, ncol = 2)
```
